---
title: "Week 3 assignment - plotly"
author: "Martin Richardson - October 25, 2017"
output: ioslides_presentation
#output: html_document
runtime: shiny
---


```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(plotly)
library(datasets)
```

## The Chatterjee-Price Attitude Data

From a survey of the clerical employees of a large financial organization, the data are aggregated from the questionnaires of the approximately 35 employees for each of 30 (randomly selected) departments. The numbers give the percent proportion of favourable responses to seven questions in each department. 

```{r}
names(attitude)
```

This data set contains an overall satisfaction rating (referred to as "rating") as well as six specific rating categories. Any five of these seven quantities can be added to the following plot, whether as x/y/z-axes, marker colour or marker size.


## (3+2)-Dimensional plot

```{r, echo = FALSE, cache = TRUE}
df <- attitude
```

```{r echo = FALSE}
inputPanel(
  selectInput(inputId = "x_var", label = "Choose x-axis", 
              choices = c("rating", "complaints", "privileges", 
                          "learning", "raises", "critical", "advance"), 
              selected = "rating"),
  
  selectInput(inputId = "y_var", label = "Choose y-axis", 
              choices = c("rating", "complaints", "privileges", 
                          "learning", "raises", "critical", "advance"), 
              selected = "complaints"),
  
  selectInput(inputId = "z_var", label = "Choose z-axis", 
              choices = c("rating", "complaints", "privileges", 
                          "learning", "raises", "critical", "advance"), 
              selected = "privileges")
  )

inputPanel(
  selectInput(inputId = "colour_var", label = "Choose marker colour", 
              choices = c("rating", "complaints", "privileges", 
                          "learning", "raises", "critical", "advance"), 
              selected = "learning"),
  
  selectInput(inputId = "size_var", label = "Choose marker size", 
              choices = c("rating", "complaints", "privileges", 
                          "learning", "raises", "critical", "advance"), 
              selected = "raises")
)
```

```{r warning = FALSE, message = FALSE, echo = FALSE}
renderPlotly({

  x_var      <- input$x_var
  y_var      <- input$y_var
  z_var      <- input$z_var
  colour_var <- input$colour_var
  size_var   <- input$size_var

  p <- plot_ly(df, x = df[[x_var]], y = df[[y_var]], z = df[[z_var]],
          type = "scatter3d", mode = "markers",
          color = df[[colour_var]], size = df[[size_var]])

  p
  })  
```

